Block bootstrap consistency\\under weak assumptions

### 2016-09-28 subs/ETr3/reply_3.tex
[#24] Add AucTeX variables to referee 3 letter
[#20] Draft reply to referee re: notation
[#27] Tweak centering term in Brownian Motion
Related to issue #20, I think it makes sense to center on a different
variable. This commit changes the centering term and revises my letter
to the referee.
Make small changes to referee letter

In your letter, you wrote,
\begin{quotation}
  \noindent\textit{``Yes, your array notation is of course needed to
    accommodate the assumption of mean heterogeneity. However, what I
    was really hoping for was some additional transparency in the form
    of an example of a mean array which would satisfy Assumption 2 of
    Theorem 1, and also perhaps a case which would fail to satisfy
    it.}

@@

You also wrote,
\begin{quotation}
  \noindent\textit{``Just one additional comment on the text. On page
    5, line --7, should $\mu_n^*$ read $\bar{\mu}_n^*$?''}
\end{quotation}
\end{document}

>>>>

In your report, you wrote,
\begin{quotation}
  \noindent\textit{``Yes, your array notation is of course needed to
    accommodate the assumption of mean heterogeneity. However, what I
    was really hoping for was some additional transparency in the form
    of an example of a mean array which would satisfy Assumption 2 of
    Theorem 1, and also perhaps a case which would fail to satisfy
    it.}

@@

Thank you for clarifying this. I have added new material that explains
when these assumptions are satisfied when there is a single break in
the mean of the stochastic process. Specifically, it explains how the
break size and break timing can affect whether the assumptions
hold. This section starts half-way through page 4 and is a bit more
than half a page long.

Working through this example revealed that the original assumption
on the means was too restrictive, so I have also relaxed the
assumption on the the dispersion of the means from
$\sum_t (\mu_{nt} - \bar \mu_n)^2) \to 0$ to
$\sum_t (\mu_{nt} - \bar \mu_n)^2) = o(n p_n^2)$ (using notation for
the stationary bootstrap; the assumption has been relaxed for all
three of the block bootstraps considered).  This change does not
affect the mathematical proofs very much: I have added a very simple
result (Lemma 3) that shows that the contribution of the $\mu_{nt}$'s to the
second moment of $\bar X^*$ remains asymptotically negligible under
this assumption and strengthened one of the components of Lemma 1.

The proofs of Lemmas 4 and 6 (which were labeled Lemmas 3 and 5 in the
last version of the paper) have to be changed a little as well to
reflect the new assumption on $\mu_{nt}$. The previous version of
Lemma 6 established that (suitably normalized) $Z_i^2$s are uniformly
integrable and used that as an intermediate result to show that the
$Z_i^{*2}$s are also u.i.\ under the right normalization. The new
version skips that intermediate step (the family of $Z_i^2s$ are no
longer u.i.) but uses components of the original proof to show that
the $Z_i^{*2}$s are u.i. directly. The relaxed assumption on the
dispersion of the $\mu_{nt}$s ensures that the blocks are short
enough that the stronger assumption continues to hold for the
$\mu_{nt}^*$s.
Changing the proof in this way essentially amounts to rearranging the
elements of the original proof and invoking the new Lemma 3.

To help make the changes as clear as possible, I have uploaded a
pdf based on `latexdiff' that highlights the differences in the
two versions as a supplemental document. I have also made a few
spelling and wording corrections that will be apparent as well.

You also wrote,
\begin{quotation}
  \noindent%
  \textit{``Just one additional comment on the text. On page
    5, line --7, should $\mu_n^*$ read $\bar{\mu}_n^*$?''}
\end{quotation}
\noindent%
Yes, thank you, this was an error. I've changed $\mu_n^*$ to
$E^* \bar X_n^*$ to highlight the connection with Theorem 1's results.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
